Supporting Information

### 2018-02-27 SupportingInformation.Rmd
it runs, also rearranged aphid count and ff results into separate sections

---
output:
  pdf_document: default
---
---
title: "Supporting Information"
author: "Shyamolina Ghosh and Daniel Reuman"
date: "February 12, 2018"
geometry: "left=1cm,right=1cm,top=2.5cm,bottom=2.8cm"

@@

We fitted several copulas
and got AIC values and upper- and lower-tail dependency estimates based on the fitted copulas:
```{r soilCNfit,echo=F}
h<-BivMS_res_Loecke$InfCritRes[,c("copname","AICw","BICw","LTdep","UTdep")]
table_nums("soilCNfit",display=F)
knitr::kable(h, caption = "Fitting info for soil C and N dataset. Here and henceforth copula names are abbreviated as: N=normal (Gaussian); C=Clayton; G=Gumbel; F=Frank; J=Joe; SC=Survival Clayton; SG=Survival Gumbel; SJ=Survival Joe. An S in front of one of the copulas BB1, BB6, BB7, BB8 indicates the survival version of that copula (rotation by 180 degrees).")
```
`r table_nums("soilCNfit",display="c")` shows that several copulas are much better supported (higher AIC and BIC weights) than the Gaussian copula, answering the first part of question 1 for these data.

@@

## Aphid data
<!--Shya to edit the prentation below to make it more parallel to the presentation of the model selection results for C/N data above-->

@@

Count results

@@

```{r count_AICw,echo=F,results="asis"}

cat("\n\n\\pagebreak\n")

table_nums("count_AICw",display=F)
knitr::kable(RES_aphid_count$info_ord_AICw[,,1], caption = "Aphid_count : AICw for best fit copula family for each selective location pair")
```

@@

First flight results

```{r ff_LTdep,echo=F,results="asis"}
cat("\n\n\\pagebreak\n")

table_nums("ff_LTdep",display=F)
knitr::kable(RES_aphid_ff$info_ord_LTdep[,,1], caption = "Aphid_firstflight : Lower Tail dependence for best fit copula family for each selective location pair")
```

@@

# Count results
```{r stat_aphid_count, echo=F, cache=T, cache.extra=list(seed,data_aphid_count)}
set.seed(seed) 
resloc<-"./Results/stat_results/stat_aphid_count/"

@@

# First flight results

@@

<!--
# Question 2 analyses for each dataset

# Question 3 analyses for each dataset
-->

>>>>

---
title: "Supporting Information"
author: "Shyamolina Ghosh and Daniel Reuman"
date: "February 12, 2018"
geometry: "left=1cm,right=1cm,top=2.5cm,bottom=2.8cm"

@@

We fitted several copulas
and got AIC values and upper- and lower-tail dependency estimates based on the fitted copulas:
```{r soilCNfit,echo=F}
h<-BivMS_res_Loecke$InfCritRes[,c("copname","AICw","BICw","LTdep","UTdep")]
table_nums("soilCNfit",display=F)
knitr::kable(h, caption = "Fitting info for soil C and N dataset. Here and henceforth copula names are abbreviated as: N=normal (Gaussian); C=Clayton; G=Gumbel; F=Frank; J=Joe; SC=Survival Clayton; SG=Survival Gumbel; SJ=Survival Joe. An S in front of one of the copulas BB1, BB6, BB7, BB8 indicates the survival version of that copula (rotation by 180 degrees).")
```

`r table_nums("soilCNfit",display="c")` shows that several copulas are much better supported (higher AIC and BIC weights) than the Gaussian copula, answering the first part of question 1 for these data.

@@

## Aphid abundance data 
<!--Add common and species name to header-->

@@

@@

```{r count_AICw,echo=F,results="asis"}
table_nums("count_AICw",display=F)
knitr::kable(RES_aphid_count$info_ord_AICw[,,1], caption = "Aphid_count : AICw for best fit copula family for each selective location pair")
```

@@

@@

```{r stat_aphid_count, echo=F, cache=T, cache.extra=list(seed,data_aphid_count)}
set.seed(seed) 
resloc<-"./Results/stat_results/stat_aphid_count/"

@@

## Aphid first flight data
<!--Add species common name and scientific name to header-->

```{r ff_LTdep,echo=F,results="asis"}
table_nums("ff_LTdep",display=F)
knitr::kable(RES_aphid_ff$info_ord_LTdep[,,1], caption = "Aphid_firstflight : Lower Tail dependence for best fit copula family for each selective location pair")
```

### Non-parametric analysis of tail dependence

@@

# Question 2 analyses for each dataset

# Question 3 analyses for each dataset
